Efficient Calculation of Polynomial and Interaction Features on Sparse Matrices

### 2015-09-22 paper/paper2.tex
made more clear

Notice that, for an individual row, the location of a polynomial feature ($\id{row}i \cdot \id{row}j$) can be determined
by a simple counter $k$ that is incremented each pass through the inner loop. This cannot be
done if we only calculate products between nonzero elements of $\vec{x}$, because all that
will be known is the nonzero element indices - many iterations will be skipped (hence the improved computational complexity).

>>>>

Notice that, for an individual row, the location of a polynomial feature ($\id{row}[i] \cdot \id{row}[j]$) can be determined
by a simple counter $k$ that is incremented each pass through the inner loop. This cannot be
done if we only calculate products between nonzero elements of $\vec{x}$, because all that
will be known is the nonzero element indices - many iterations will be skipped (hence the improved computational complexity).
